Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-03-25 content.tex
Spellcheck

There have been multiple attempts to investigate the importance of tree
prior choice. For example, recently Sarver et al., [\cite{sarver2019choice}] 
showed that the choice of tree prior does not 
substantially affect phylogenetic inferences of diversification rates.
Also recently, Duchene et al. [\cite{duchene2018phylodynamic}] released
a BEAST2 package to assess how well posterior predictive simulations 
recover a given tree when using the standard diversification models.
These studies show how current diversification models compare to one another, 
but they do not help to assess the importance of a new tree prior.

@@

The first step simulates an alignment from the given 
phylogeny (Fig.~\ref{fig:pipeline}, 1a $\rightarrow$ 2a).
For the sake of clarity, here we will assume the alignment consists out
of DNA sequences, but other heritable material such as amino acids also works.
The user must specify a root sequence, a mutation rate and a site model.
The root sequence is the DNA sequence of the shared common ancestor of 
all species, and is set to four different equally-sized 
mononucleotide blocks by default, 
which helps interpreting the resulting alignment.
Supported nucleotide substitution models (part of a DNA
site model) are JC, HKY, TN and GTR (see Table \ref{tab:options} for
the meaning of these abbreviatons).
JC is the default nucleotide subsitution mode (NSM),
in which the nucleotide substition rates between all
nucleotides are equal and constant over time.

>>>>

There have been multiple attempts to investigate the importance of tree
prior choice. For example, recently Sarver and colleagues, [\cite{sarver2019choice}] 
showed that the choice of tree prior does not 
substantially affect phylogenetic inferences of diversification rates.
Also recently, Duchêne and colleagues [\cite{duchene2018phylodynamic}] released
a BEAST2 package to assess how well posterior predictive simulations 
recover a given tree when using the standard diversification models.
These studies show how current diversification models compare to one another, 
but they do not help to assess the importance of a new tree prior.

@@

The first step simulates an alignment from the given 
phylogeny (Fig.~\ref{fig:pipeline}, 1a $\rightarrow$ 2a).
For the sake of clarity, here we will assume the alignment consists out
of DNA sequences, but other heritable material such as amino acids also works.
The user must specify a root sequence, a mutation rate and a site model.
The root sequence is the DNA sequence of the shared common ancestor of 
all species, and is set to four different equally-sized 
mononucleotide blocks by default, 
which helps interpreting the resulting alignment.
Supported nucleotide substitution models (part of a DNA
site model) are JC, HKY, TN and GTR (see Table \ref{tab:options} for
the meaning of these abbreviations).
JC is the default nucleotide substitution mode (NSM),
in which the nucleotide substitution rates between all
nucleotides are equal and constant over time.
